### 2016-06-29 testbed.tex
.

All \ac{Raspi}s will be running an \ac{SSH} daemon for easy remote access
within the university network. We therefore had the university's \ac{IT}
department configure the university's \ac{DHCP} server to assign each \ac{Raspi} a
static \ac{IP}. This eliminates the requirements for monitors and keyboards
for the \ac{Raspi}s for non-graphical applications.
%This significantly eases the management of the \ac{Raspi}s
%as \ac{SSH} eliminates the need for monitors and keyboards for the \ac{Raspi}s.

A sketch of the testbed is depicted in Figure~\ref{fig:testbed_setup}.
The testbed is intended for students to perform simulations and measurements
as part of semester projects. We therefore intend to configure all
\ac{Raspi}s identically, while still allowing students to alter how each
\ac{Raspi} behaves and is configured.

The following produre explains a way to setup the testbed to facilitates these
requirements. The procedure is assumed to be performed by whom we will refer
to as the testbed administrator in a \ac{PC} running Linux. The exact Linux
distribution is does not matter, but the procedure will be based on
Debian Linux.

The testbed should be available for students to perform simulations and
measurements as part of their semester projects. We intend to configure
all \ac{Raspi}s identically, while still allowing students to alter
how each \ac{Raspi} behaves and is configured.

When working on the testbed with this many devices, it may not always be
desired to make persistent changes to devices. We present how the concept
of stacked filesystems may be used to enable the means of both persistent
and temporary storage.

>>>>

All \ac{Raspi}s will be configured to run a \ac{SSH} daemon for easy remote access
within the university network. We therefore had the university's \ac{IT}
department configure the university's \ac{DHCP} server to assign each \ac{Raspi} a
static \ac{IP}. This eliminates the requirements for monitors and keyboards
for the \ac{Raspi}s for non-graphical applications.
%This significantly eases the management of the \ac{Raspi}s
%as \ac{SSH} eliminates the need for monitors and keyboards for the \ac{Raspi}s.

A sketch of the testbed is depicted in Figure~\ref{fig:testbed_setup}.
The testbed is intended for students to perform simulations and measurements
as part of semester projects. We intend to configure all
\ac{Raspi}s identically, while still allowing students to alter how each
\ac{Raspi} behaves and is configured.

The following section propose a procedure to setup the testbed to facilitates these
requirements. The procedure is performed, by whom we will refer
to as the testbed administrator, in a regular \ac{PC} running Linux. The exact Linux
distribution does not matter although the procedure will be based on
Debian Linux. All the commands in this paper will be performed on
the testbed administrators \ac{PC}.

The procedure goes as follows. Based on a regular Raspbian Linux image, it will
be explained how it can be customized to include desired packages and
configured as desired.
When working on a testbed with many devices, it may not always be desired to make
persistent changes to devices. We therefore present how the concept of stacked
filesystems may be used to enable the meands of both persistent and temporary
storage. This step of the procedure will be optional if the testbed
administrator decides to write the whole image to a memory card.
Writing the whole Linux filesystem to memory cards may complicate the
maintenance as e.g. updates need to be performed in each \ac{Raspi}.
\texttt{Python Fabric} may ease this task, but we also propose alternative
approach where the initial \ac{RAM} filesystem is customized in a way that
enables \ac{Raspi}s to fetch the its root filesystem from a \ac{HTTP}
server. This enables the testbed administrator to only update the filesystem
in one location. The \ac{Raspi}s will then get the changes after a reboot.

%\textcolor{red}{The testbed should be available for students to perform simulations and
%measurements as part of their semester projects. We intend to configure
%all \ac{Raspi}s identically, while still allowing students to alter
%how each \ac{Raspi} behaves and is configured.
%\\\\
%When working on the testbed with this many devices, it may not always be
%desired to make persistent changes to devices. We present how the concept
%of stacked filesystems may be used to enable the means of both persistent
%and temporary storage.}
